\documentclass[letter, 10pt, conference]{ieeeconf}

\IEEEoverridecommandlockouts

\overrideIEEEmargins

\usepackage{amssymb,url,amsmath}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{color}
\usepackage{ifpdf}
\usepackage{url}
\usepackage{enumerate}
\usepackage{array}
\usepackage{flushend}
\usepackage{multirow,booktabs}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{mdwlist}
\usepackage[utf8]{inputenc}
\usepackage{tcolorbox}
\newcommand{\alg}{Algorithm~}
\newtcolorbox[auto counter]{algorithmbox}[2][]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries, title=\alg\thetcbcounter: #2,#1}

\newcommand{\eq}{Eq.~}
\newcommand{\fig}{Fig.~}
\newcommand{\tab}{Tab.~}
\newcommand{\sect}{Sec.~}

\newcommand{\re}{R}
\newcommand{\rf}{R}
\newcommand{\rl}{L}
\newcommand{\om}{O}
\newcommand{\cm}{M}
\newcommand{\fm}{F}
\newcommand{\hc}{C}
\newcommand{\rg}{G}
\newcommand{\qd}{Q}
\newcommand{\gpm}{T}
\newcommand{\coll}{W}
\newcommand{\pdf}{\mathbf{pdf}}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{argmax}}\medspace}

\graphicspath{{images/}}

\title{\LARGE \bf
Learning and Inference of Dexterous Grasps for Novel Objects with Underactuated Hands
}

\author{Marek Kopicki$^{1}$ and Carlos J. Rosales$^{2}$ and Hamal Marino$^{2}$ and Marco Gabiccini$^{2}$ and Jeremy L. Wyatt$^{1}$% <-this % stops a space
\thanks{*This work was supported by EC-FP7-ICT-600918, PacMan.}% <-this % stops a space
\thanks{$^{1}$Marek Kopicki and Jeremy L. Wyatt are with the Intelligent Robotics Laboratory, School of Computer Science,
        University of Birmingham, Birmingham, B15 2TT, UK.}
        %{\tt\small \{msk,jlw\}@cs.bham.ac.uk}}%
\thanks{$^{2}$Carlos J. Rosales, Hamal Marino and Marco Gabiccini are with Centro Piaggio, Universita di Pisa, Pisa, Italy.}
               %{\tt\small carlos.rosales@for.unipi.it, hamal.marino@centropiaggio.unipi.it, m.gabiccini@ing.unipi.it}}%
\thanks{Correspond to: {\tt\small M.S.Kopicki at cs.bham.ac.uk}}%
}
\begin{document}


\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Recent advances have been made in learning of grasps for fully actuated hands. A typical approach learns the target locations of finger links on the object. When a new object must be grasped, new finger locations are generated, and a collision free reach-to-grasp trajectory is planned. Such a division of labour fails to transfer directly to underactuated hands, which improve grasp reliability via contacts with the object during grasping. In this paper we present a method for learning transferrable grasps for underactuated hands. Our approach learns not only the desired final grasp, and also good grasping trajectories, from a rigid body simulation. This enables us to learn how to approach the object and close the underactuated hand from a variety of poses. Our method does not rely on explicit representation of the contact sequence. The core learning method uses product of experts. This allows grasp transfer to novel objects and works despite partial shape reconstruction of less than 25\% of the surface. From nine training grasps on three objects the method transferred grasps to previously unseen, novel objects, that differ significantly from the training objects, with an 80\% success rate. We move beyond previous work by: i) showing the ability to learn transferrable grasps for underactuated hands; ii) extending our learning method to work with multiple training examples for each grasp type; iii) extending our method to work with multiple reach to grasp trajectories.
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:introduction}
\input{./inputTex/introduction.tex}

%!TEX root = dexterous-grasping-sage-style.tex

\section{OVERVIEW OF APPROACH}
\label{sec:overview}
\input{./inputTex/overview.tex}

\section{BASIC REPRESENTATIONS}
\label{sec:representations}
\input{./inputTex/representations.tex}

\section{DATA GENERATION}
% SAY HOW WE USE THE SIMULATOR HERE
\input{./inputTex/learning.tex}

\section{INFERENCE}
\label{sec:infer}
% NEED TO ADAPT FOR SOFT HAND (TRAJECTORY + CONTACT MODEL)
\input{./inputTex/inference.tex}

\section{RESULTS}
\label{sec:results}
% DESCRIBE EXPERIMENTS
\input{./inputTex/results.tex}

 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
%\bibliography{bibliography/carlos,bibliography/ref1,bibliography/ref2}
%% THERE ARE REPEATED ENTRIES IN REF1 AND REF2
\bibliography{bibliography/carlos,bibliography/ref1,bibliography/ref2}

\addtolength{\textheight}{-12cm}

%\section*{APPENDIX}
%
%
%\section*{ACKNOWLEDGMENT}


\end{document}
