\documentclass[a4paper, 10pt, conference]{ieeeconf}

\IEEEoverridecommandlockouts

\overrideIEEEmargins

\usepackage{amssymb,url,amsmath}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{color}
\usepackage{ifpdf}
\usepackage{url}
\usepackage{enumerate}
\usepackage{array}
\usepackage{flushend}
\usepackage{multirow,booktabs}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{mdwlist}
\usepackage[utf8]{inputenc}
\usepackage{tcolorbox}
\newcommand{\alg}{Algorithm~}
\newtcolorbox[auto counter]{algorithmbox}[2][]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries, title=\alg\thetcbcounter: #2,#1}

\newcommand{\eq}{Eq.~}
\newcommand{\fig}{Fig.~}
\newcommand{\tab}{Tab.~}
\newcommand{\sect}{Sec.~}

\newcommand{\re}{R}
\newcommand{\rf}{F}
\newcommand{\rl}{L}
\newcommand{\om}{O}
\newcommand{\cm}{M}
\newcommand{\fm}{F}
\newcommand{\hc}{C}
\newcommand{\rg}{G}
\newcommand{\qd}{Q}
\newcommand{\gpm}{T}
\newcommand{\coll}{W}
\newcommand{\pdf}{\mathbf{pdf}}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{argmax}}\medspace}

\graphicspath{{images/}}

\title{\LARGE \bf
Learning and Inference of Dexterous Grasps for Novel Objects with Underactuated Hands
}

\author{Marek Kopicki$^{1}$ and Carlos J. Rosales$^{2}$ and Hamal Marino$^{2}$ and Marco Gabiccini$^{2}$ and Jeremy L. Wyatt$^{1}$% <-this % stops a space
\thanks{*This work was supported by EC-FP7-ICT-600918, PacMan.}% <-this % stops a space
\thanks{$^{1}$Marek Kopicki and Jeremy L. Wyatt are with the Intelligent Robotics Laboratory, School of Computer Science,
        University of Birmingham, Birmingham, B15 2TT, UK.}
        %{\tt\small \{msk,jlw\}@cs.bham.ac.uk}}%
\thanks{$^{2}$Carlos J. Rosales, Hamal Marino and Marco Gabiccini are with Centro Piaggio, Universita di Pisa, Pisa, Italy.}
               %{\tt\small carlos.rosales@for.unipi.it, hamal.marino@centropiaggio.unipi.it, m.gabiccini@ing.unipi.it}}%
\thanks{Correspond to: {\tt\small M.S.Kopicki at cs.bham.ac.uk}}%
}
\begin{document}


\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Recent advances have been made in learning of grasps for fully actuated hands. A typical approach learns the target locations of finger links on the object. When a new object must be grasped, new finger locations are generated, and a collision free reach-to-grasp trajectory is planned. This assumes a collision free trajectory to the final grasp. This is not possible with underactuated hands, which cannot be guaranteed to avoid contact, and in fact exploit contacts with the object during grasping, so as to reach an equilibrium state in which the object is held securely. Unfortunately these contact interactions are i) not directly controllable, and ii) hard to monitor during a real grasp. We overcome these problems so as to permit learning of transferrable grasps for underactuated hands. We make two main technical innovations. First, we model contact interactions during the grasp implicitly. We do this by modelling motor commands that lead reliably to the equilibrium state, rather than modelling contact changes themselves. This alters our reach-to-grasp model. Second, we extend our contact model learning algorithm to work with multiple training examples for each grasp type. This requires the ability to learn which parts of the hand reliably interact with the object during a particular grasp. Our approach learns from a rigid body simulation. This enables us to learn how to approach the object and close the underactuated hand from a variety of poses. From nine training grasps on three objects the method transferred grasps to previously unseen, novel objects, that differ significantly from the training objects, with an 80\% success rate. 
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:introduction}
\input{./inputTex/introduction.tex}

%!TEX root = dexterous-grasping-sage-style.tex

\section{OVERVIEW OF APPROACH}
\label{sec:overview}
\input{./inputTex/overview.tex}

\section{BASIC REPRESENTATIONS}
\label{sec:representations}
\input{./inputTex/representations.tex}

\section{DATA GENERATION}
% SAY HOW WE USE THE SIMULATOR HERE
\input{./inputTex/learning.tex}

\section{INFERENCE}
\label{sec:infer}
% NEED TO ADAPT FOR SOFT HAND (TRAJECTORY + CONTACT MODEL)
\input{./inputTex/inference.tex}

\section{RESULTS}
\label{sec:results}
% DESCRIBE EXPERIMENTS
\input{./inputTex/results.tex}

 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
%\bibliography{bibliography/carlos,bibliography/ref1,bibliography/ref2}
%% THERE ARE REPEATED ENTRIES IN REF1 AND REF2
\bibliography{bibliography/carlos,bibliography/ref1,bibliography/ref2}

\addtolength{\textheight}{-12cm}

%\section*{APPENDIX}
%
%
%\section*{ACKNOWLEDGMENT}


\end{document}
